\documentclass{letter}
\address{Roy Triggs\\ South Devon, UK}
\signature{Yours Sincerely,\\Roy Triggs}
\begin{document}
\begin{letter}
{Resourcing Team\\Met Office\\South West England\\EX1 3PB}
\opening{Dear Resourcing Team,}

I write you a letter, expressing my strong interest in the Exploiting K-Scale data for machine learning development Industrial Placement 2026. As a recent graduate with a Bachelor's honours degree in Mathematics and Economics at the University of Liverpool and currently pursuing my MSc in Data Science and Artificial Intelligence, I am eager to contribute my technical skills and passion for innovation to your esteemed organization.

I would love to work at the Met Office for a number of reasons. Firstly, the Met Office's dedication to use their resources as a force for good, aligns perfectly with my own values. I am particularly excited about the chance to use science and data to benefit society and protect the environment. Secondly, this project on exploiting K-Scale data for machine learning was inspiring to me, because I thoroughly enjoyed working with large datasets and preparing them for machine learning applications during my studies. Finally, your commitment to fostering a collaborative, inclusive environment and prioritising growth in expertise and the evolution of science resonate with my personal values and professional goals and I find this highly motivating.

During my academic journey, I have built a strong foundation in programming languages such as Python and GitHub, along with expertise in data analysis, designing experiments using machine learning methods, and model evaluation. My coursework and projects have sharperned my ability handle complex problems, identify and apply appropriate techniques, and work collaboratively in team environments. For example, one recent project investigated the trade off between exploration and exploitation in reinforcment learning, I led a team to develop a robust Q-learning algorithm to optimise decision-making processes for a multi-armed bandit. In addition to my technical skills, I have a strong communication and problem-solving abilities, I presented our key findings to my professor and peers, effectively conveying complex concepts in an understandable manner. I have consistently excelled in group projects, honsing my leadership and teamwork skills, and I am confident in my ability to organise tasks and meet deadlines efficiently.

I am eager to bring my technical expertise, passion for betterment, and collaborative spirit to the Met Office and contribute to the success of the K-Scale data project. I would welcome the opportunity to demonstrate this at the next stage of the recruitment process.

Thankyou for considering my applicaiton.

\closing{I look forward to your reply,}

\end{letter}

\end{document}